Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip.tex
Fix minor bug

	Ingredients:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the X-Z local Hamiltonian instance associated with the computation of $C'(x)$ from \Cref{thm:LHReduction}.
		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item \XW{Let $s=n+T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem. But I forgot to count ancilla, so this currently isn't correct.}
		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{41}\lambda^2}{\varepsilon^{51}}$ copies \Ethan{$505=2\times 7\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\varepsilon^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name. Nobody has defined/used this register before.} \XW{this is the Z measurement?} \Ethan{Yeah} of $\rho_i$ under the standard basis and save the outcome as $z$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{1}{192}\frac{\varepsilon^2}{\sum_i\abs{\alpha_i}}$, then the verifier outputs $(\Acc, z)$.
			Else, it outputs $(\Rej, \bot)$.
	\end{enumerate}
\end{protocol}

>>>>

	Ingredients:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}=\sum_i \alpha_i H_i$ be the X-Z local Hamiltonian instance associated with the computation of $C'(x)$ from \Cref{thm:LHReduction}.
		\item Let $\histpsi{{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item \XW{Let $s\leq n+2T+\frac{6T}{\varepsilon}$ be the number of qubits in $\ket{\psi_{C'(x)}}$ Why this number?} \Ethan{This number is used in de Finetti theorem. But I forgot to count ancilla, so it wasn't correct.}
		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item\label{step:qpip1-state-gen} The honest prover prepares $M=649\frac{T^{41}\lambda^2}{\varepsilon^{51}}$ copies \Ethan{$649=2\times 9\times 6\times 6+1$} of $\histpsi{C'(x)}$ and sends all of it to the verifier qubit-by-qubit.
		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{20}\lambda}{\varepsilon^{24}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name. Nobody has defined/used this register before.} \XW{this is the Z measurement?} \Ethan{Yeah} of $\rho_i$ under the standard basis and save the outcome as $z$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{1}{192}\frac{\varepsilon^2}{\sum_i\abs{\alpha_i}}$, then the verifier outputs $(\Acc, z)$.
			Else, it outputs $(\Rej, \bot)$.
	\end{enumerate}
\end{protocol}
